---
title: "Orientation"
author: "Ama Owusu-Darko"
date: "`r Sys.Date()`"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r dbi}
library(DBI)
library(tidyverse)
library(tidylog)

```

```{r drops}
#Wrangling Roche data from online
Roche_Pipeline <- read_delim("C:/Users/Korantema/Downloads/Roche_Pipeline_2024-01-09 (1).csv",delim = ";", escape_double = FALSE, trim_ws = TRUE)

Roche_Pipeline<-Roche_Pipeline|>
  filter(!is.na(`Trade name`)&!is.na(`Filing date`)&`Filing date`!='2025+')
```

```{r db}
#Load R dataframe into the database
DBI::dbWriteTable(mydb,"roche_products", Roche_Pipeline)
DBI::dbListTables(mydb)

DBI::dbDisconnect(mydb)

```

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r ui, echo=FALSE}
library(shiny)
library(shinyjs)

# Connecting to a database
mydb <- dbConnect(RSQLite::SQLite(), "roche_products")
generateColumn <- function(year) {
  column(textOutput(outputId = paste0("resultDisplay", year)), width = 3)
}

ui <- fluidPage(
  titlePanel("Roche Pipeline"),
  sidebarLayout(
    sidebarPanel(),
    mainPanel(
      fluidRow(
        generateColumn(2020),
        generateColumn(2021),
        generateColumn(2022),
        generateColumn(2023)
      )
    )
  )

)

# Define server function
server <- function(input, output, session) {
  
  # Query the 'roche_products' table and fetch the count where "Filing date" is the specified year
  queryResult <- function(year) {
    outputName <- paste0("resultDisplay", year)
    
    output[[outputName]] <- renderText({
      as.character(dbGetQuery(mydb, paste('SELECT COUNT(*) FROM roche_products WHERE "Filing date" =', year)))
    })
  }

  
  # Call the updateText function for each year
  updateText(2020)
  updateText(2021)
  updateText(2022)
  updateText(2023)
  
  # Close the database connection when the Shiny app stops
  session$onSessionEnded(function() {
    dbDisconnect(mydb)
  })
}

# Create the app object
shinyApp(ui = ui, server = server)

```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
#shinyAppDir(
 # system.file("examples/06_tabsets", package = "shiny"),
 # options = list(
 #   width = "100%", height = 550
 # )
#)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.


```{r}
library(shiny)
library(DBI)
library(shinyjs)  
#Connecting to a database
mydb <- dbConnect(RSQLite::SQLite(), "roche_products")
ui <- fluidPage(
  useShinyjs(),  # Initialize shinyjs

  titlePanel("Database Query Result"),
  mainPanel(
    textOutput("resultDisplay"),
    actionButton("unhideButton", "Unhide Result")  # Button to unhide the result
  )
)

server <- function(input, output, session) {
  observeEvent(invalidateLater(45000, session), {
    wordIndex <- isolate(as.numeric(input$wordIndex))

    # Change the word every 45 seconds
    wordIndex <- if (wordIndex == 1) 2 else 1

    # Update the word index in the hidden input
    updateTextInput(session, "wordIndex", value = as.character(wordIndex))

    # Query the database and update the result display
    result <- if (wordIndex == 1) {
      "2020"
    } else {
      # Query the 'roche_products' table and fetch the count where "Filing date" is 2020
      query_result <- dbGetQuery(con, 'SELECT COUNT(*) FROM roche_products WHERE "Filing date" = 2020')
      paste("Count of rows with 'Filing date' equal to 2020: ", query_result$`COUNT(*)`)
    }

    # Update the result display
    output$resultDisplay <- renderText(result)
  })

  # Unhide the result when the "Unhide" button is clicked
  observeEvent(input$unhideButton, {
    shinyjs::toggle("resultDisplay")
  })


  # Close the database connection when the Shiny app stops
  session$onSessionEnded(function() {
    dbDisconnect(mydb)
  })
}

shinyApp(ui, server)

```

